A generalized definition of multidimensional item response theory parameters

### 2022-10-27 output/paper_draft/paper_M2PLM_parameters.Rmd
Update with Mario's review, until start of Proposition 1 (WIP)

Our aim is to find the point of maximum slope of $`r IRF_ABBR`$ in
$`r LATENT_SPACE`$. As in @reckase_difficulty_1985, we need to
reparameterize Equation \@ref(eq:M2PL-formulation) in polar coordinates,
because the slope is dependent on the direction considered.
However, Reckase's Equation 3 implicitly assumes orthogonality.
In order to contemplate the general case,
we need to introduce a few linear algebra results before proceeding futher.

@@

Let's consider the standard basis $`r LS_STD_BASIS_EQ`$ in $`r LATENT_SPACE`$.
TODO: Incomplete in Mario's version, is it correct to say "in the latent space"?
We can write all $`r TRAIT_VEC_IN_LS`$ as a linear combination of each baseis.
Therefore, we have both representations: $`r TRAIT_VECTOR_DEF_BASIS_EQ`$, and
$`r TRAIT_VECTOR_DEF_STD_BASIS_EQ`$, where $`r TRAIT_COORDS_EQ`$ and
$`r TRAIT_COORDS_STD_EQ`$.

@@

The $`r DIM_INDEX`$-th column of $`r TRANSFORM_MATRIX`$

with $`r TRAIT_VECTOR_STD`$ the coordinates
of $`r TRAIT_VECTOR`$ in $`r LATENT_SPACE_STD`$ and $`r TRANSFORM_MATRIX_EQ`$
(being $`r BASIS_VECTOR_ANY_TRANSF`$ the coordinates of
$`r BASIS_VECTOR_ANY`$ in $`r LATENT_SPACE_STD`$
for any dimension $`r DIM_INDEX`$).
This new space can be defined as a Euclidean space with standard inner product
(i.e. dot product), such that the norm $`r NORM_EQ`$ of $`r TRAIT_VECTOR`$
in $`r LATENT_SPACE_STD`$ is given by<!-- # TODO: Reference needed? -->

\begin{equation}
  `r TRAIT_MODULE`^2 = `r TRAIT_VECTOR_STD_SQ` =
    `r TRANSF_TRAIT_SQUARED` =
    `r TRAIT_TRANSF_TRAIT`.                                 (\#eq:inner-product)
\end{equation}

Thus, the inner product matrix $`r INNER_PROD_MATRIX`$ in $`r LATENT_SPACE`$
is consistently defined as

\begin{equation}
  `r INNER_PROD_MAT_EQ`.                            (\#eq:inner-prod-matrix-def)
\end{equation}

### Direction cosines

@@

>>>>

Our aim is to find the point of maximum slope of $`r IRF_ABBR`$ in
$`r LATENT_SPACE`$. As in @reckase_difficulty_1985, we need to
reparameterize Equation \@ref(eq:M2PL-formulation) in polar coordinates,
because the slope is dependent on the direction considered.
However, Reckase's Equation 3 implicitly assumes orthogonality.
In order to contemplate the general case,
we need to introduce a few linear algebra results before proceeding further.

@@

Let's consider the standard basis $`r LS_STD_BASIS_EQ`$ in $`r LATENT_SPACE`$.
<!-- TODO: Incomplete in Mario's version, is it correct to say "in the latent space"? -->
We can write all $`r TRAIT_VEC_IN_LS`$ as a linear combination of each baseis.
Therefore, we have both representations: $`r TRAIT_VECTOR_DEF_BASIS_EQ`$, and
$`r TRAIT_VECTOR_DEF_STD_BASIS_EQ`$, where $`r TRAIT_COORDS_EQ`$ and
$`r TRAIT_COORDS_STD_EQ`$.

@@

The $`r DIM_INDEX`$-th column of $`r TRANSFORM_MATRIX`$ is given by the
coordinates of $`r BASIS_VECTOR_ANY`$ in basis $`r LS_STD_BASIS`$.
<!-- # TODO: For all k? -->
If $`r BASIS_VECTOR_ANY_TRANSF_EQ`$, then

\begin{equation}
  `r TRANSFORM_MATRIX_EQ`.                           (\#eq:transform-matrix-def)
\end{equation}

With the standard basis in $`r LATENT_SPACE`$ we have the usual scalar product<!-- (i.e. dot product) -->.
With basis $`r LS_BASIS`$ in $`r LATENT_SPACE`$ we define an inner product
$`r LS_BASIS_INNER_PROD`$, such that the norm of $`r TRAIT_VECTOR`$ is
invariant, i.e., $`r TRAIT_NORM_EQ`$. Therefore,

\begin{equation}
  `r TRAIT_NORM_STD_SQ_EQ`.                             (\#eq:inner-product-def)
\end{equation}

Thus, we must define the inner product $`r LS_BASIS_INNER_PROD`$ with Gram
matrix $`r INNER_PROD_MAT_EQ`$. That is, $`r INNER_PROD_EQ`$, which keeps the
norm invariant.

The Gram matrix has $`r INNER_PROD_MAT_ELEMENT_EQ`$ as element. As
$`r TRANSFORM_MATRIX`$ (and consequently $`r TRANSFORM_MATRIX_TRANSP`$) is
invertible, so $`r INNER_PROD_MATRIX`$ is, and $`r INNER_PROD_MATRIX_INV_EQ`$.

@@

Let's consider now the vectors $`r DIR_COS_VEC`$ and $`r DIR_COS_VEC_STD`$, made
up by the $`r N_DIMS`$ direction cosines of $`r TRAIT_VECTOR`$ with the basis
vectors of $`r LS_BASIS`$ and $`r LS_STD_BASIS`$, respectively.

::: {#prp-cosines-equivalence}

**Proposition 1.** Under the previously defined conditions, for all
$`r TRAIT_VEC_IN_LS`$,

with

:::
